The complex network of trophic interactions in a subAntarctic Marine Protected Area

### 2023-01-20 1st_Manuscript/ManuscriptDraft.Rmd
Figures 4 & 5

# Figure
a <- plot_totdeg
b <- plot_preddeg
c <- plot_preydeg
d <- plot_grpdeg

# Move to a new page
grid.newpage()
# Nested ggarrange
ggarrange(a,                                                                                         # First row
          ggarrange(b, c, ncol = 2, labels = c("B", "C"), font.label=list(color="black",size=30)),   # Second row
          ggarrange(d, ncol = 1),                                                                    # Third row
          nrow = 3, labels = "A",
          font.label=list(color="black",size=30))

@@

```{r figure4, echo=FALSE}
# Betweenness, Closeness & Trophic similarity by Trophic level

@@

>>>>

# Arrange figure
a <- plot_totdeg
b <- plot_preddeg
c <- plot_preydeg
d <- plot_grpdeg

# Move to a new page
grid.newpage()
# Nested ggarrange
figure_3 <- ggarrange(a,                                                                                         # First row
          ggarrange(b, c, ncol = 2, labels = c("B", "C"), font.label=list(color="black",size=30)),   # Second row
          ggarrange(d, ncol = 1),                                                                    # Third row
          nrow = 3, labels = "A",
          font.label=list(color="black",size=30))
figure_3

@@

```{r figure4, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Species-level properties (A) betwenness, (B) closeness, and (C) trophic similarity by trophic level (equal or greater than 2). See table 1 for definitions and ecological relevance."}
# Betweenness, Closeness & Trophic similarity by Trophic level (>= 2)

# Betweenness
plot_sp_bt <- spp_total %>% 
  filter(TL >= 2) %>% 
  ggplot(., aes(x = TL, y = Between)) +
  geom_point() +
  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
  labs(x = "Trophic level", y = "Betweenness") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 26),
        axis.text.y = element_text(size = 26),
        axis.title = element_text(size = 26, face = "bold"))

# Closeness
plot_sp_cl <- spp_total %>% 
  filter(TL >= 2) %>%
  ggplot(., aes(x = TL, y = Close)) +
  geom_point() +
  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
  labs(x = "Trophic level", y = "Closeness") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 26),
        axis.text.y = element_text(size = 26),
        axis.title = element_text(size = 26, face = "bold"))

# Trophic similarity
plot_sp_ts <- spp_total %>% 
  filter(TL >= 2) %>%
  ggplot(., aes(x = TL, y = meanTrophicSimil)) +
  geom_point() +
  #geom_vline(xintercept = c(spp_nt_12+1, spp_nt_12+spp_nt_13+1, spp_nt_14+1), linetype = "longdash", colour = "red") +
  labs(x = "Trophic level", y = "Trophic similarity") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 26),
        axis.text.y = element_text(size = 26),
        axis.title = element_text(size = 26, face = "bold"))

# Move to a new page
grid.newpage()
# Arrange figure
figure_4 <- ggarrange(plot_sp_bt + rremove("xlab"), plot_sp_cl + rremove("xlab"), plot_sp_ts + rremove("xlab"),
                      labels = c("A","B","C"), ncol=2, nrow=2,
                      font.label = list(size = 30, color = "black"))
annotate_figure(figure_4, bottom = textGrob("Trophic level", gp = gpar(fontface="bold", col="black", fontsize=26)))

@@

top.role.col <- hcl.colors(4, palette = "Purple-Green")
TRColor <- setNames(top.role.col, levels(as.factor(V(g_up)$TopRole)))
TRColor <- as.data.frame(TRColor) %>% 
  mutate(TopRole = c("hubcon", "modcon", "modhub", "modspe"))
#show_col(top.role.col)  # shows color & code
data_TRColor <- spp_total %>% 
  dplyr::select(TopRole, everything()) %>% 
  left_join(TRColor)
g_up_c <- g_up %>% 
  set_vertex_attr("TRColor", value = data_TRColor$TRColor)

# Filter network connectors ('hubcon') & module connectors ('modcon'). Violet & pink respectively
sp_con <- spp_total %>% 
  filter(TopRole == "hubcon" | TopRole == "modcon")

# Move to a new page
grid.newpage()
# Arrange figure
figure_5 <- plot_troph_level(g_up_c, vertexLabel = F, modules = F, ylab = "Trophic level", vertex.color = V(g_up_c)$TRColor)
